A SIMPLE NUMERICALLY STABLE PRIMAL-DUAL ALGORITHM FOR COMPUTING NASH-EQUILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION

### 2015-10-15 paper.tex
multiple glitches

% Title.
% ------
\title{A SIMPLE PRIMAL-DUAL ALGORITHM FOR COMPUTING APPROXIMATE
  NASH-EQUAILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}

@@

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash-equilibria in two-person zero-sum sequential games with
incomplete information and perfect recall (like Texas Hold'em
Poker). Our algorithm is numerically stable, performs basic
iterations (i.e matvec multiplications, clipping, etc., and no calls
to external first-order oracles, no matrix inversions, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with incomplete information
and perfect recall. The
applicability to the latter kind of games is thanks to the
sequence-form representation which allows us to encode any such game
as a matrix game with convex polytopial strategy profiles. We prove
that the number of iterations needed to produce a Nash-equilibrium
with a given precision is inversely proportional to the precision. As
proof-of-concept, we present experimental results on matrix games
on simplexes and Kuhn Poker.
\end{abstract}

\begin{keywords} Nash-equilibrium, sequential games,
  incomplete information, perfect recall, convex optimization
\end{keywords}

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists of computing Nash-equilibria (in fact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. In this
paper, we propose a simple primal-dual algorithm for solving for such
equilibria approximately (in a sense to be made precise in Definition
\ref{thm:cool_notion} below).

@@

The LCPs above have the equivalent saddle-point formulation
\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle,
  \label{eq:gilpin}
\end{equation}
where the \textit{convex polytope} (by which we mean a bounded convex
polyhedron)
\begin{equation}
  Q_k := \{z \ge 0 |\text{ }E_kz = e_k\} \subseteq
  [0, 1]^{n_k}
\label{eq:polytope}
\end{equation}
is identified with the strategy profile of player $k$ in the
sequence-form representation. At a feasible point $(y, p, x, q)$ for
the LCPs, the \textit{primal-dual gap} $\tilde{G}(y, p, x, q)$ is
given by\footnote{The first inequality being due to \textit{weak
    duality}.}
\begin{eqnarray}
  \begin{split}
  0 &\le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
gap for the equivalent saddle-point problem \eqref{eq:gilpin}.
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\begin{split}
\hspace{.25em} -Ay + E_1^Tp \ge 0, &\hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0,\\
&\langle y, A^Tx  + E_2^Tq\rangle = 0.
\end{split}
\label{eq:feasibility}
\end{equation}
Moreover, at equilibria, \textit{strong duality} holds and the value
of the game equals $p_0 = -q_0$, i.e the primal-dual gap
$\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
equilibria.%%  Solving the LCPs \eqref{eq:primal_pb} and
%% \eqref{eq:dual_pb} exactly is very practice
%% \cite{koller1992complexity}) and such a precision doesn't have any
%% fundamental practical advantage. Instead, it is customary compute
%% ``approximate'' Nash-equilibria.%%  A now introduce a popular notion of
%% %% approximate Nash-equilibria:

\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans for which there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

@@

\subsection{Notation and terminology}
\paragraph*{General.} Let $m$ and $n$ be positive integers.
The components of a vector $z \in \mathbb{R}^n$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
\sqrt{\langle z, z\rangle}$. $(z)_+:=\text{max}(0, z) \in
\mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
function. The $n$-simplex denoted $\Delta_n$, is defined by $\Delta_n
:= \{z \in \mathbb{R}^n_+|\sum_j z_j = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph*{Convex analysis.} Let us introduce some basic but powerful
modern convex-analytical
notions which will be essential in the sequel. Given a subset $C$ of
$\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined
by $i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise}$.
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). For example, we will write $i_{z \ge 0}$ for
$i_{\mathbb{R}^n_+}(z)$, etc.  The \textit{orthogonal projector} onto $C$, is the
``closest-point'' map $\proj_C: \mathbb{R}^n \rightarrow C, x
  \mapsto \underset{z \in
      C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
Let $f : \mathbb{R}^n \rightarrow
(-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
defined by
$\partial f(x) := \{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z -
x\rangle, \forall z \in \mathbb{R}^n\}$.
%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
%% in case $f$ is differentiable at $x$.
If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
  \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z)$.
%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
%% operators generalize orthogonal projectors. For example
%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
%% (z)_+$. One also has the useful characterization
%% \begin{eqnarray}
%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
%% \end{eqnarray}
%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
%% should) be thought of as performing an \textit{implicit} gradient step
%% of size $\gamma$.

The interested reader should refer to \cite{combettes2011proximal} and
the references therein, for a more elaborate exposition on
proximal calculus. % and its use in modern convex-optimization.

\subsection{A remark concerning matrix games on simplexes.} It should
be noted
that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game, and so the
results presented in this manuscript can be trivially applied such
games in particular. For this special sub-class of sequential games,
the primal-dual gap function $G(x,y)$ writes
\begin{eqnarray}
\begin{split}
G(x, y) &=
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\}\\
&= \underset{0 \le i <
  n_1}{\text{max }}(Ay)_i - \underset{0 \le j < n_2}{\text{min
}}(A^Tx)_j.
\end{split}
\label{eq:mg_pd}
\end{eqnarray}

\subsection{Quick sketch of our contribution}
%% One cannot directly attack the LCPs
%% \eqref{eq:primal_pb} and
%% \eqref{eq:dual_pb} via a traditional primal-dual algorithm
%% (for example \cite{chambolle2010,chambolle2014ergodic}) because
%% computing the orthogonal projections $\proj_{Q_k}$ is very difficult
%% In fact, such sub-problems would have to be solved
%% iteratively\footnote{An ``exception to the rule'' is the case where
%%   the $Q_k's$ are simplexes, so that the projections can be computed
%%   exactly using \cite{duchi2008efficient}.}.
We now give a brief overview of our contributions, which will be made
more elaborate in section \ref{sec:gsp}.
Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologous to that presented in Definition \ref{thm:approx_nash}, we
device a simple numerically stable primal-dual algorithm that
(Algorithm \ref{Tab:algo}) for computing approximate Nash-equilibria
in sequential two-person zero-sum games with incomplete information and
perfect recall. On, each iteration, the only operations performed by
our algorithm are of the form $A^Tx$, $Ay$, $E_1^Tp$, $E_2^Tq$, and
$(x)_+$. We also prove (Theorem \ref{thm:pd}) that --in an ergodic /
Ces\`ario sense-- the number of iterations required by the algorithm
to produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$, with explicit values for the constants
involved.
%% The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.
% These contributions will be elaborated in section \ref{sec:gsp}.

\section{Relation to prior work}
\label{sec:related_work}
Here, we present a selection of algorithms that is representative of the
efforts that have been made in the literature to compute Nash
$\epsilon$-equilibria for two-person zero-sum games with incomplete
information like Texas Hold'em Poker, etc.
First and foremost, let us note that for the class of games considered
here (sequential games with incomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP and interior-point solvers can
handle (see for example \cite{hoda2010smoothing,gilpinfirst}).

\subsection{Regret minimization}
CFR (CounterFactual Regret minimization) \cite{zinkevich2008regret},
Monte Carlo CFR \cite{lanctot2009monte}, and CFR+
\cite{Bowling09012015}, by their large popularity, have become the
definitive state-of-the-art, and are particularly useful in
many-player games, since convex-analytical methods cannot help much in
such games. Also, they can be shown to converge to a Nash-equilibrium
provided each player uses a CFR scheme to play the game
\cite{zinkevich2008regret}, but have a much weaker
convergence theory. For example, \cite{lanctot2009monte} showed that
such scheme have a running time of $\mathcal{O}(1/\epsilon^2)$ to
produce a Nash $\epsilon$-equilibrium.

\subsection{First-order methods}
In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} (EGT and
precursors are well-known to the signal-processing community
\cite{NESTA}) was used
to solve the equilibrium problem \eqref{eq:gilpin}.
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop.
\cite{gilpinfirst} proposed a modified version of the techniques in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log \left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. The crux of their technique was to
observe that \eqref{eq:gilpin} can further be written a the minimization of
the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:dgap})
for the game\footnote{The minimizers of $G$ are precisely the
  equilibria of the game.}, viz
\begin{eqnarray}
\mathrm{minimize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
\end{eqnarray}
and then show there exists a scalar
$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
\begin{eqnarray}
\text{``distance between }(x, y)\text{ and the set of
equilibria'' } \le G(x, y)/\delta.
\end{eqnarray}
Their
algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
with a geometrically decreasing sequence of tolerance levels
$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
should be noted however that
\begin{itemize}
\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log\left(1 / \epsilon\right)\right)$ convergence rate can
be arbitrarily large for ill-conditioned games.
\item[--] The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Most
  notably, the complicated projections $\proj_{Q_k}$ are applied at
  each iteration.%%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.
\end{itemize}
Recently, \cite{kroer2015} proposed accelerations to first-order
methods for computing Nash-equilibria (including those just
discussed), by an appropriate choice of the underlying \textit{Bregman
distance} and the \textit{distance generating function} (essential
ingredients in EGT-type algorithms). These modifications provably
gain a constant factor in the worst-case convergence rate of the
resulting algorithm. %, compared to \textit{vanilla} implementations.

\subsection{Primal-dual algorithms}
The primal-dual algorithm first developed in \cite{chambolle2010}, was
proposed in \cite{chambolle2014ergodic} as a way of solving matrix
games on simplexes. Notably, such matrix games on
simplexes are considerably simpler than the games considered
here. Indeed, the authors in \cite{chambolle2014ergodic} used the fact
that computing the orthogonal projection of a point onto a simplex can
be done in linear time as in \cite{duchi2008efficient}. In contrast,
no such efficient algorithm is known nor is likely to exist, for the
polytopes $Q_k$ defined in \eqref{eq:polytope}. %% , the strategy
%% profiles for players in %% the games considered here.
That notwithstanding, such projections can still be done iteratively
using for example, the algorithm in proposition 4.2 of
\cite{combettes2010dualization} or the algorithms developed in
\cite{tran2015splitting}. Unfortunately, as with any nested iterative
scheme, one would have to solve this sub-problem with finer and finer
precision, rendering the overall solver impractical.

>>>>

% Title.
% ------
\title{A SIMPLE NUMERICALLY STABLE PRIMAL-DUAL ALGORITHM FOR COMPUTING
  NASH-EQUILIBRIA IN SEQUENTIAL GAMES WITH INCOMPLETE INFORMATION}

@@

\maketitle
\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash-equilibria in two-person zero-sum sequential games with
incomplete information and perfect recall (like Texas Hold'em
Poker). Our algorithm is numerically stable, performs only basic
iterations (i.e matvec multiplications, clipping, etc., and no calls
to external first-order oracles, no matrix inversions, etc.), and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with incomplete information
and perfect recall. The applicability to the latter kind of games is
thanks to the sequence-form representation which allows us to encode
any such game as a matrix game with convex polytopial strategy
profiles. We prove that the number of iterations needed to produce a
Nash-equilibrium with a given precision is inversely proportional to
the precision. As proof-of-concept, we present experimental results on
matrix games on simplexes and Kuhn Poker.
\end{abstract}

\begin{keywords} Nash-equilibrium, sequential games,
  incomplete information, perfect recall, convex optimization
\end{keywords}
%\tableofcontents
\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists of computing Nash-equilibria (in fact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. In this
paper, we propose (our detailed contributions are sketched in
subsection \ref{sec:sketch} below and elaborated in section
\ref{sec:gsp}) a simple primal-dual algorithm for solving for such
equilibria approximately (in a sense to be made precise in Definition
\ref{thm:cool_notion} below).

@@

The LCPs above have the equivalent saddle-point formulation
\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle,
  \label{eq:gilpin}
\end{equation}
where the compact convex polytope
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k} | z \ge 0, E_kz = e_k\} \subseteq
  [0, 1]^{n_k}
\label{eq:polytope}
\end{equation}
is identified with the strategy profile of player $k$ in the
sequence-form representation. At a feasible point $(y, p, x, q)$ for
the LCPs, the \textit{duality gap} $\tilde{G}(y, p, x, q)$ is
given by\footnote{The first inequality being due to \textit{weak
    duality}.}
\begin{eqnarray}
  \begin{split}
  0 &\le \tilde{G}(y, p, x, q) := \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
gap for the equivalent saddle-point problem \eqref{eq:gilpin}.
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a
Nash-equilibrium for the game)  if and only if there exist vectors $p$
and $q$ such that
\begin{equation}
\begin{split}
\hspace{.25em} -Ay + E_1^Tp \ge 0, &\hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0,\\
&\langle y, A^Tx  + E_2^Tq\rangle = 0.
\end{split}
\label{eq:feasibility}
\end{equation}
Moreover, at equilibria \textit{strong duality} holds and the value
of the game equals $p_0 = -q_0$, i.e the duality gap
$\tilde{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
equilibria.%%  Solving the LCPs \eqref{eq:primal_pb} and
%% \eqref{eq:dual_pb} exactly is very practice
%% \cite{koller1992complexity}) and such a precision doesn't have any
%% fundamental practical advantage. Instead, it is customary compute
%% ``approximate'' Nash-equilibria.%%  A now introduce a popular notion of
%% %% approximate Nash-equilibria:

\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans for which there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the duality gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

@@

\subsection{A remark concerning matrix games on simplexes}
It should be noted that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$
specifies a matrix game with payoff matrix $A$, for which player $k$'s
strategy profile is a simplex
\begin{eqnarray}
\Delta_{n_k} := \left\{z \in \mathbb{R}^{n_k}|z \ge 0,\sum_j
z_j = 1\right\}.
\end{eqnarray}
This simplex can be written as a compact convex polytope in
the form \eqref{eq:polytope} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game, and so the
results presented in this manuscript can be trivially applied such
games in particular. For this special sub-class of sequential games,
the duality gap function $G(x,y)$ writes
\begin{eqnarray}
\begin{split}
G(x, y) &=
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\}\\
&= \underset{0 \le i <
  n_1}{\text{max }}(Ay)_i - \underset{0 \le j < n_2}{\text{min
}}(A^Tx)_j.
\end{split}
\label{eq:mg_pd}
\end{eqnarray}

\subsection{Quick sketch of our contribution}
\label{sec:sketch}
%% One cannot directly attack the LCPs
%% \eqref{eq:primal_pb} and
%% \eqref{eq:dual_pb} via a traditional primal-dual algorithm
%% (for example \cite{chambolle2010,chambolle2014ergodic}) because
%% computing the orthogonal projections $\proj_{Q_k}$ is very difficult
%% In fact, such sub-problems would have to be solved
%% iteratively\footnote{An ``exception to the rule'' is the case where
%%   the $Q_k's$ are simplexes, so that the projections can be computed
%%   exactly using \cite{duchi2008efficient}.}.
We now give a brief overview of our contributions, which will be made
more elaborate in section \ref{sec:gsp}.
Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologous to that presented in Definition \ref{thm:approx_nash}, we
device a simple numerically stable primal-dual algorithm that
(Algorithm \ref{Tab:algo}) for computing approximate Nash-equilibria
in sequential two-person zero-sum games with incomplete information and
perfect recall. On, each iteration, the only operations performed by
our algorithm are of the form $A^Tx$, $Ay$, $E_1^Tp$, $E_2^Tq$, and
$(x)_+ := (\max(0, x_j))_j$. We also prove (Theorem \ref{thm:pd}) that
--in an ergodic / Ces\`ario sense-- the number of iterations required
by the algorithm to produce an approximation equilibrium to a
precision $\epsilon$ is $\mathcal{O}(1/\epsilon)$, with explicit
values for the constants involved.
%% The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.
% These contributions will be elaborated in section \ref{sec:gsp}.

\subsection{Notation and terminology}
\paragraph*{General.} Let $m$ and $n$ be positive integers.
The components of a vector $z \in \mathbb{R}^n$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). $\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ }
z \geq 0\}$ is the nonnegative $n$th \textit{orthant}.
$\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| :=
\sqrt{\langle z, z\rangle}$. %%  $(z)_+:=\text{max}(0, z) \in
%% \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For
%% example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$. The
%% operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp}
%% function.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph*{Convex analysis.} %% For our purposes, it will suffice to
%% know the following basic but powerful modern convex-analytical
%% concepts. The interested reader should refer to
%% \cite{combettes2011proximal} and the references therein for a more
%% elaborate and scholastic exposition on the subject. % and its use in
%%                                 % modern
%%                                 % convex-optimization.
Given a subset $C \subseteq \mathbb{R}^n$, $i_C$ denotes the
\textit{indicator function} of $C$ defined by $i_C(x) = 0 \text{ if }
x \in C\text{ and }+\infty\text{ otherwise}$.
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). For example, we will write $i_{z \ge 0}$ for
$i_{\mathbb{R}^n_+}(z)$, etc.  The \textit{orthogonal projector} onto
$C$, is the ``closest-point'' map $\proj_C: \mathbb{R}^n \rightarrow
C, x \mapsto \underset{z \in C}{\text{argmin }}\frac{1}{2}\|z-x\|^2$.
Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
$dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$.
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subdifferential} of $f$ at a point $x \in \mathbb{R}^n$ is
defined by
$\partial f(x) := \{v \in \mathbb{R}^n | f(z)  \ge f(x) + \langle v, z -
x\rangle, \forall z \in \mathbb{R}^n\}$.
%% Each element of $\partial f(x)$ is called a \textit{subgradient} of $f$
%% at $x$. Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
%% in case $f$ is differentiable at $x$.
If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by $\prox_f(x): = \underset{z \in
  \mathbb{R}^n}{\text{argmin }}\frac{1}{2}\|z
  - x\|^2 + f(z)$.
%% For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
%% $\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
%% operators generalize orthogonal projectors. For example
%% $\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
%% (z)_+$. One also has the useful characterization
%% \begin{eqnarray}
%%   p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
%% \end{eqnarray}
%% Thus given $\gamma > 0$, the operator $\prox_{\gamma f}$ can (and
%% should) be thought of as performing an \textit{implicit} gradient step
%% of size $\gamma$.

We recommend \cite{rockafellar1997convex,combettes2011proximal} for a
more detailed exposition on convex analysis and its use in
modern optimization theory and practice.

\section{Relation to prior work}
\label{sec:related_work}
Here, we present a selection of algorithms that is representative of the
efforts that have been made in the literature to compute Nash
$\epsilon$-equilibria for two-person zero-sum games with incomplete
information like Texas Hold'em Poker, etc.
It should be noted that the class of games considered
here (sequential games with incomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP and interior-point solvers can
handle (see \cite{hoda2010smoothing,gilpinfirst}).

\subsection{Regret minimization}
CFR (CounterFactual Regret minimization) \cite{zinkevich2008regret},
Monte Carlo CFR \cite{lanctot2009monte}, and CFR+
\cite{Bowling09012015}, by their large popularity, have become the
definitive state-of-the-art, and are particularly useful in
many-player games, since convex-analytical methods cannot help much in
such games. Also, they can be shown to converge to a Nash-equilibrium
provided each player uses a CFR scheme to play the game
\cite{zinkevich2008regret}, but have a much weaker
convergence theory. For example, \cite{lanctot2009monte} showed that
such schemes have a prohibitive running time of
$\mathcal{O}(1/\epsilon^2)$ to produce a Nash $\epsilon$-equilibrium.

\subsection{First-order methods}
In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} (EGT and
precursors are well-known to the signal-processing community
\cite{NESTA}) was used
to solve the equilibrium problem \eqref{eq:gilpin}.
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop.
\cite{gilpinfirst} proposed a modified version of the techniques in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) \log \left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. The crux of their technique was to
observe that \eqref{eq:gilpin} can further be written a the minimization of
the duality gap function $G(x, y)$ (defined in \eqref{eq:dgap})
for the game\footnote{The minimizers of $G$ are precisely the
  equilibria of the game.}, viz
\begin{eqnarray}
\mathrm{minimize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
\end{eqnarray}
and then show there exists a scalar
$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
\begin{eqnarray}
\text{``distance between }(x, y)\text{ and set of
equilibria'' } \le G(x, y)/\delta.
\end{eqnarray}
Their
algorithm is then derived by iteratively applying Nesterov smoothing
\cite{nesterov2005a}
with a geometrically decreasing sequence of tolerance levels
$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)
$G$. However, there are a number of issues, most notably: \textit{(a)}
The constant $\delta > 0$ can be arbitrarily small, and so the factor
$\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| / \delta\right)
\log\left(1 / \epsilon\right)\right)$ convergence rate can be
arbitrarily large for ill-conditioned games.
\textit{(b)} The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Most
  notably, projections onto the polytopes $Q_k$ are computed on
  each iteration, a very hard sub-problem. %%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.

Recently, \cite{kroer2015} proposed accelerations to first-order
methods for computing Nash-equilibria (including those just
discussed), by an appropriate choice of the underlying \textit{Bregman
distance} and the \textit{distance generating function} (essential
ingredients in EGT-type algorithms). These modifications provably
gain a constant factor in the worst-case convergence rate over the
original algorithm. %, compared to \textit{vanilla} implementations.

\subsection{Primal-dual algorithms}
The primal-dual algorithm first developed in \cite{chambolle2010}, was
proposed in \cite{chambolle2014ergodic} as a way of solving matrix
games on simplexes. Notably, such matrix games on
simplexes are considerably simpler than the games considered
here. Indeed, the authors in \cite{chambolle2014ergodic} used the fact
that computing the orthogonal projection of a point onto a simplex can
be done in linear time as in \cite{duchi2008efficient}. In contrast,
no such efficient algorithm is known nor is likely to exist, for the
polytopes $Q_k$ defined in \eqref{eq:polytope}. %% , the strategy
%% profiles for players in %% the games considered here.
That notwithstanding, such projections can still be done iteratively
using for example, the algorithm in proposition 4.2 of
\cite{combettes2010dualization} or the algorithms developed in
\cite{tran2015splitting}. Unfortunately, as with any nested iterative
scheme, one would have to solve this sub-problem with finer and finer
precision, rendering the overall solver impractical. One can also cite
\cite{nurminski2008}, in which the authors endeavored an iterative
projection algorithm onto polytopes in outer representation.
